Maximum Entropy Spectral Analysis: a case study

### 2021-06-07 paper/referee_response.md

- It’s not really clear to me when you perform the forecasting for the temperature data why CAT is the obvious choice for the loss function, since in the previous section you described how CAT is unable to recover the true order of the autoregressive process. Does that mean that it would be worse at forecasting based on the AR(p)? There seems to be a contradiction where CAT does a better job for the temperature data but worse for the simulation presented in section II. It would be helpful to elaborate on this.
	+ We added a claryfing footnote on this (note 10, page 10). We hope it is clearer now.

- "Indeed, a precise prediction of the strain time series can be beneficial in the detection of anomalies in the data and, eventually, their removal.”: How does this compare to the method presented in https://arxiv.org/abs/1908.05644, where the data containing a glitch are “inpainted” with values chosen such that the inverse-PSD-filtered data is 0 at these times?
	+ To answer this matter is not easy and this should be addressed in future works. Thanks for pointing out the reference: we added it

### Final Remarks and Future Prospects

- In addition to adding the citations to other LVC works presenting methods and results for marginalizing over the PSD uncertainty (see PnP comments above), a more detailed discussion of how MESA compares to these other methods (particularly the error in the PSD measurement) would be appropriate here.
	+ We believe we discussed in details the matter in section 4, which we refer the reader to. At the beginning of the section, we addeed two lines explaining why the comparison shall be qualitative (being the results very problem dependent, we believe that every measure of error hardly generalises to other problems).

### 2021-06-07 paper/mesa.tex
Some edits to the paper-bis

\section{Comparison with Welch method}\label{sec:Welch_comparison}
\sschmidt{Do we want to make a comparison with BayesLine? I think so... \\ Do we want to introduce this method in the introduction? Makes sense}
In this section we perform a qualitative comparison between the performance of the MESA and of the standard Welch algorithm.
Although similar studies can be drawn from any other PSD, for definiteness, we focus on the analytical PSD computed for LIGO Handford interferometer, released together with the GWCT-1 catalog~\citep{GWTC1, PSD_release}, and computed with BayesLine package \citep{Cornish_2015, Littenberg_2015, Cornish_2020, Chatziioannou_2019}.

>>>>

\section{Comparison with Welch method}\label{sec:Welch_comparison}
We perform a {\it qualitative} comparison between the performance of the MESA and of the standard Welch algorithm.
In this, we cannot avoid to be only qualitative. Indeed, as the results of the comparison are problem dependent, it is very hard to quantify this in a single metric. Although similar studies can be drawn from any other PSD, in this section we focus on a single PSD and we try to generalize some observations that we make.
We decide to use the analytical PSD computed for LIGO Handford interferometer, released together with the GWCT-1 catalog~\citep{GWTC1, PSD_release}, and computed with BayesLine package \citep{Cornish_2015, Littenberg_2015, Cornish_2020, Chatziioannou_2019}.
